### 2022-11-10 NSF2022/Description/backgroundv2.tex

\begin{wrapfigure}[12]{r}{0.5\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-5pt}
\caption{\label{fig:amphiphilic_assembly}
Self-organization under amphiphilic boundary condition.
(a) Granules first match hydrophobic tails (red),
(b) then align length-wise.
The principle of self-organization holds in three dimensions 
as simulated by Kohl, Corona, and Veerapaneni
\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
There are downsides to traditional models in terms of generality and physical realism.
(i) Motivated by drug delivery applications, experimenters use electric
fields, for example, to controllably open and close pores in membranes
\cite{}.
These kinds of topological changes are clumsy to incorporate in
sharp interface formulations that assume a continuous surface \cite{}.
(ii) Sharp-interface models assume a membrane of neglible thickness. 
However, in biological processes
like fusion, fission, or insertion and penetration by proteins and peptides, 
the length scales of the
deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm).
Moreover, these processes crucially rely on variable lipid
orientation relative to the surface normal (the so-called \emph{tilt}
deformation),
whereas \eqref{eq:Canham-Helfrich} implicitly assumes that the lipids
are everywhere normal to the surface.  
(iii) Finally, realistic membranes are comprised of a mixtures of lipids and proteins.
Recent work \cite{} has incorporated lipid mixtures in \eqref{eq:Canham-Helfrich},
but these models are formidably complicated 
due to the additional constraints and transport equations involved.

Diffusive interface models and surface-director models partially address 
these shortcomings. 
Topological changes are permitted in phase field and level set formulations,
but these methods smear out the details of lipid orientations.
The detailed energies of lipid orientation that include tilt are
closely related to the celebraated and well-studied
field of nematic liquid crystals.  Here, there have been recent development
in simulation and theory of nematic liquid crystals on surfaces.
These models consider the interplay between defects and surface geometry \cite{},
finite element formulations \cite{}, and existence of minimizers \cite{}.

@@

\begin{wrapfigure}[11]{r}{0.5\textwidth}
\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\caption{\label{fig:JPv_linearshear}The JP vesicles undergo tank-treading in background shear flow.}
\end{wrapfigure}
\textit{Summary of results from the paper \cite{Fu2018_SIAM}.}
A striking aspect of the
model is its fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to realistic values,
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}.
\emph{Bending:}
The bending deformation enters through the splay of the
granule directors.  In Figure \ref{fig:JPv_linearshear},
for example, the directors have negative, respectively positive,
splay $\nabla_{\Sigma} \cdot \dd$
in the outer, respectively inner monolayers.
Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
is the surface divergence for the unit normal $\NN$
and the splay energy density
for the granule configuration is Hookean with bending modulus $k_B$.
It is a fact from differential geometry that
when $\dd$ is everywhere parallel to $\NN,$
then $\nabla\cdot \dd = \pm 2H$ and this is how the
curvature term arises for \eqref{eq:Canham-Helfrich}
($2H = \kappa$ in the two-dimensional setting).
In the case of mixtures of granules of different sizes,
spontaneous curvature $k_0$ arises
from asymmetry in the monolayer leaflets.
\emph{Stretching.}
When stretched, the distance between
neighboring granules is increased from rest
and the energy for stretching behaves as 
$\tfrac{1}{2}k_A(L - L_0)^2/L_0$
for a stretching modulus $k_A$,
length $L$, and
length at rest $L_0$ of the two-dimensional vesicle. 
\emph{Tilt.}
Finally, the granules possess a 
tilt decay length scale $\lambda = \sqrt{k_B/k_{\theta}}$
well-known from the biophysical literature
for the case when the directors $\mathbf{d}$ are no longer normal
to the surface
\cite{KUZMIN2005}.

\textit{Summary of results from the paper \cite{FuQuRyYo22}.}

\begin{wrapfigure}[14]{l}{0.475\textwidth}
%\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture}The JP vesicles rupture under large shear rates.}
\end{wrapfigure}

>>>>

There are downsides to traditional models in terms of generality and physical realism.
(i) Motivated by drug delivery applications, experimenters use electric
fields, for example, to controllably open and close pores in membranes
\cite{}.
These kinds of topological changes are clumsy to incorporate in
sharp interface formulations that assume a continuous surface \cite{}.
(ii) Sharp-interface models assume a membrane of neglible thickness. 
However, in biological processes
like fusion, fission, or insertion and penetration by proteins and peptides, 
the length scales of the
deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm).
Moreover, these processes crucially rely on variable lipid
orientation relative to the surface normal (the so-called \emph{tilt}
deformation),
whereas \eqref{eq:Canham-Helfrich} implicitly assumes that the lipids
are everywhere normal to the surface.  
(iii) Finally, realistic membranes are comprised of a mixtures of lipids and proteins.
Recent work \cite{} has incorporated lipid mixtures in \eqref{eq:Canham-Helfrich},
but these models are formidably complicated 
due to the additional constraints and transport equations involved.

\begin{wrapfigure}[12]{r}{0.5\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-5pt}
\caption{\label{fig:amphiphilic_assembly}
Self-organization under amphiphilic boundary condition.
(a) Granules first match hydrophobic tails (red),
(b) then align length-wise.
The principle of self-organization holds in three dimensions 
as simulated by Kohl, Corona, and Veerapaneni
\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
Diffusive interface models and surface-director models partially address 
these shortcomings. 
Topological changes are permitted in phase field and level set formulations,
but these methods smear out the details of lipid orientations.
The detailed energies of lipid orientation that include tilt are
closely related to the celebraated and well-studied
field of nematic liquid crystals.  Here, there have been recent development
in simulation and theory of nematic liquid crystals on surfaces.
These models consider the interplay between defects and surface geometry \cite{},
finite element formulations \cite{}, and existence of minimizers \cite{}.

@@

\begin{wrapfigure}[11]{r}{0.5\textwidth}
\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\caption{\label{fig:JPv_linearshear}Granular vesicles undergo
tank-treading in background shear flow.}
\end{wrapfigure}
\textit{Summary of results from the paper \cite{Fu2018_SIAM}.}
A striking aspect of the
model is its fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to realistic values,
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}.
\emph{Bending:}
The bending deformation enters through the splay of the
granule directors.  In Figure \ref{fig:JPv_linearshear},
for example, the directors have negative, respectively positive,
splay $\nabla_{\Sigma} \cdot \dd$
in the outer, respectively inner monolayers.
Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
is the surface divergence for the unit normal $\NN$
and the splay energy density
for the granule configuration is Hookean with bending modulus $k_B$.
It is a fact from differential geometry that
when $\dd$ is everywhere parallel to $\NN,$
then $\nabla\cdot \dd = \pm 2H$ and this is how the
curvature term arises for \eqref{eq:Canham-Helfrich}
($2H = \kappa$ in the two-dimensional setting).
In the case of mixtures of granules of different sizes,
spontaneous curvature $k_0$ arises
from asymmetry in the monolayer leaflets.
\emph{Stretching.}
When stretched, the distance between
neighboring granules is increased from rest
and the energy for stretching behaves as 
$\tfrac{1}{2}k_A(L - L_0)^2/L_0$
for a stretching modulus $k_A$,
length $L$, and
length at rest $L_0$ of the two-dimensional vesicle. 
\emph{Tilt.}
Finally, the granules possess a 
tilt decay length scale $\lambda = \sqrt{k_B/k_{\theta}}$
well-known from the biophysical literature
for the case when the directors $\mathbf{d}$ are no longer normal
to the surface
\cite{KUZMIN2005}.

\begin{wrapfigure}[14]{l}{0.475\textwidth}
%\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture}Rupture of a granular vesicle under large shear rates.}
\end{wrapfigure}
\textit{Summary of results from the paper \cite{FuQuRyYo22}.}
In terms of hydrodynamics, the granule vesicles in linear
background flows \eqref{eqn:shear_BG_flow} also replicates
the behaviour of an continous, inextensible,
elastic vesicle with permeability.
The simulations showed, for the first time,
a granule-vesicle suspension behaving
as a tank-treading vesicle \cite{Finken2008, Shaqfeh11}
(see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal
intermonolayer slip and derived values for intermonolayer
friction were in good quantitative agreement 
those derived by atomistic and Martini force field
simulation studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}.
In Figure \ref{fig:JPv_rupture},
membrane rupture occurs at large shear rates $\dot \gamma$
and we derived a dimensional scaling to 
predict critical shear rate for rupture
\cite{VLAHOVSKA2009775,keller_skalak_1982}.
Finally, a side-by-side comparison
of granule-based vesicles and the continuous model using
\eqref{eq:Canham-Helfrich} yielded shapes and trajectories that
basically overlapped.

### 2022-11-10 NSF2022/Description/specificaim1v2.tex

%\setcounter{page}{1}
%\addcontentsline{toc}{section}{Bibliography}
%\bibliographystyle{abbrvnat}
%%
%\bibliography{refs}
%
%
%
%\end{document}

>>>>

Our future goals include extending the current framework to a three-dimensional JP vesicle system. This will require additional algorithmic implementation including a fast summation method such as the fast multipole method. Other research directions include fluctuating hydrodynamics for Brownian suspensions (Bao et al. 2018), critical to understanding membrane diffusion, and an analysis of the relationship between particle shape on effective properties. Finally, physically more accurate boundary conditions for the HAP model will allow us to draw comparisons between computational and laboratory experiments.
